%-------------------------
% Resume in Latex
% Author : Colin Osborn
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{https://colinosborn.github.io/}{\Large Colin Osborn}} & Email : \href{mailto:colin.osborn@gmail.com}{colin.osborn@gmail.com}\\
%   \href{https://colinosborn.github.io/}{http://www.https://colinosborn.github.io} & Mobile : +1-970-618-1212 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Colin Osborn} \\ \vspace{1pt}
    \small \href{mailto: colin.osborn@gmail.com}{\underline{colin.osborn@gmail.com}} $|$ 
    \href{https://linkedin.com/in/colinosborn}{\underline{linkedin.com/in/colinosborn}} $|$
    \href{https://github.com/ColinOsborn}{\underline{github.com/ColinOsborn}}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Engineer}{March 2022 -- April 2023}
      {Forward Financing $|$ \emph{Ruby on Rails, TypeScript, React, PostgreSQL, AWS, Docker}}{Boston, Massachusetts [remote]}
      \resumeItemListStart
        \resumeItem{Successfully developed and integrated a suggested pricing automation feature, reducing manual underwriting review time by 5\% per application and reducing probability for errors.}
        \resumeItem{Contributed to intricate TypeScript frontend components and test suites, leading to notable enhancements in overall system performance, decrease in errors and improved user experience.}
        \resumeItem{Restructured ACH payment code, leading to a substantial increase in system efficiency, while also mitigating risk.}
        \resumeItem{Engineered an efficient server-side architecture, employing modular and reusable code to enhance performance and realize a substantial decrease in response times for the pricing decision engine}
        \resumeItem{Designed and implemented scalable RESTful backend APIs in Ruby, adeptly managing an ongoing stream of requests for sustained performance.}
        \resumeItem{Developed and integrated an algorithmic solution to automate user assignments, optimizing application efficiency based on role and seniority criteria.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Dec 2017 - April 2023}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Fullstack Engineer}{Aug. 2020 -- Feb. 2022}
      {PatientsLikeMe $|$ \emph{Ruby on Rails, React, PostgreSQL, GraphQL, ElasticSearch}} {Cambridge, Massachusetts [remote]}
  \resumeItemListStart
        \resumeItem{Engineered a robust user recommendation algorithm using Ruby and GraphQL, yielding tangible improvements in user engagement that were prominently displayed on the React frontend.}
        \resumeItem{Developed RESTful API endpoints for the efficient transmission of JSON data to the React frontend and external partners, achieving a noteworthy enhancement in the speed and user experience of the web application.}
        \resumeItem{Designed and executed test suites across frontend and backend layers, fortifying app performance and integrity while establishing thorough coverage of essential thresholds.}
    \resumeItemListEnd

    \resumeSubheading
      {Support Engineer}{Dec. 2017 -- April 2020}
      {Bluetent Marketing $|$ \emph{PHP, Drupal, JavaScript, SQL, SCSS, Git, Docker}}{Carbondale, CO [hybrid]}
      \resumeItemListStart
        \resumeItem{Implemented critical fixes and feature updates, fostering continuous improvement across company websites.}
        \resumeItem{Built reusable code and libraries for future use on 120 sites company-wide.}
        \resumeItem{Optimized front end UX by adding advanced JavaScript search components to search related field data fetched by calling back-end APIs.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Wax Guide} $|$ \emph{Ruby on Rails, React, PostgreSQL, Docker}}{Feb 2019 -- Present}
          \resumeItemListStart
             \resumeItem{Designed a ski-focused social network app, connecting skiers and enabling the sharing of valuable tips, conditions, and other relevant information.}
            \resumeItem{Developed a feature-rich web application that employed Ruby on Rails for the REST API and harnessed React for an interactive front-end.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Property Manager} $|$ \emph{Ruby on Rails, TypeScript, Rspec, PostgreSQL, TravisCI, Git}}{March 2022 -- Present}
          \resumeItemListStart
            \resumeItem{Engineered a user-friendly full-stack solution enabling homeowners to efficiently schedule tasks and engage in communication with property managers.}
            \resumeItem{Integrated real-time weather data from API providers to deliver precise work delay notifications.}
            \resumeItem{Developed end-to-end billing solutions empowering property managers to bill clients and contractors seamlessly.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education and Honors}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Turing School of Software}{Denver, CO}
      {Software Development}{Feb. 2016 -- Aug. 2016}
    \resumeSubheading
      {USA Cycling}{USA / Europe}
      {Former member of U23 National MTB Team}{2009}
  \resumeSubHeadingListEnd
%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Ruby, JavaScript, TypeScript, SQL (Postgres), GO, PHP, HTML, CSS} \\
     \textbf{Frameworks}{: Ruby on Rails, React, Node.js, Laravel} \\
     \textbf{Developer Tools}{: Git, Bash, Docker, TravisCI, VS Code, RubyMine, PHPstorm, Adobe Photoshop} \\
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
